---
title: "Experimentin to see if varying bin sizes can distort interpretations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 01/24/2021

## Imports

```{r}
library(readr)
library(tidyr)
library(ggplot2)
```

## Read data

```{r}
fake_data <- read_csv("fake_data.csv")
```

## Data cleaning

```{r}
fake_data_long <- gather(fake_data, key = "category", value = "value")
fake_data_long$category <- factor(fake_data_long$category, levels = c("A", "B"))
print(fake_data_long)
```

## Graph test

```{r}
ggplot(fake_data_long, aes(x = value)) +
  geom_histogram(
    color = "black",
    fill = "light blue",
    breaks = seq(10,100,15)
    ) +
  facet_grid(. ~ category)

# Useful arguments - breaks, limits, labels, trans, name
# Useful functions - scale_x_continuous

```

Next - make functions that allow quick testing of different bin configurations

### 01/30/2021

Literally just pass in the vector that represent the bins. So function-ising is not hard.

Let's try to find a way to create catch-all bins, one each at extreme left and extreme right

```{r}
bins_vector = c(
  min(fake_data_long$value),
  seq(10,100,15),
  max(fake_data_long$value)
)

ggplot(fake_data_long, aes(x = value)) +
  geom_histogram(
    color = "black",
    fill = "light blue",
    breaks = bins_vector
    ) +
  facet_grid(. ~ category) +
  scale_x_continuous(breaks = bins_vector)
```

Literally just put the max value as a bin ending :p (and same for min)

Now let's function-ise the whole logic, with variables like data_file, bins_vector. Assume that the data_file has two columns and the first row contains header names.

```{r}
make_graph <- function(data_file, bins_vector) {
  
  fake_data <- read_csv("fake_data.csv")
  fake_data_long <- gather(fake_data, key = "category", value = "value")
  fake_data_long$category <- factor(
    fake_data_long$category, levels = c("A", "B"))
  
  ggplot(fake_data_long, aes(x = value)) +
    geom_histogram(
      color = "black",
      fill = "light blue",
      breaks = bins_vector
      ) +
    facet_grid(. ~ category) +
    scale_x_continuous(breaks = bins_vector)
}
```

Test Function

```{r}
test_bins_vector = c(
  min(fake_data_long$value),
  seq(10,100,15),
  max(fake_data_long$value)
)

make_graph("fake_data.csv", test_bins_vector)
```

Done.

To do next:

1. Create a simple webapp (static, maybe with D3) that allows you to input the path of the data_file, and the bins vector.

2. Get to experimentin baby
  - Explore different data generating processes for A and B
  - Explore different bin vectors
  
  